### 2016-07-03 paper/extended-example.tex
add anything left

\begin{lstlisting}
Name = [A-Z][a-z]*

BNames = Name ", " Name (" " Name)*
Bib = ""
    | "author={" BNames (" and " BNames)* "},"

ENames = Name (" " (Name))* " " Name
End = ("%A " ENames "\n")*

@@

After completing these necessary expansions, the problem becomes synthesizing a
lens between the regular expression
\begin{lstlisting}
Bib: ""   | "author={" (" Name ", " Name (" " Name))* (" and " (" Name ", " Name (" " Name)))* "},"

End: ("%A " (Name (" " (Name))* " " Name) "\n")*
\end{lstlisting}
and

>>>>

\begin{lstlisting}
Name = [A-Z][a-z]*
Names = Name (" " Name)*

BNames = Name ", " Name Names
Bib = ""
    | "author={" BNames (" and " BNames)* "},"

ENames = Name Names " " Name
End = ("%A " ENames "\n")*

@@

After completing these necessary expansions, the problem becomes synthesizing a
lens between the regular expression
\begin{lstlisting}
Bib: ""   | ("author={" Name ", " Name Names (" and " (" Name ", " Name Names))* "},")

End: ("%A " (Name Names " " Name) "\n")*
\end{lstlisting}
and
